---
title: "Can we use SOC in the top 15cm as a proxy for SOC to 100cm deep?"
author: "CK, PR, KBD, RE & SE"
date: "25 July 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(echo = TRUE, root.dir = "C:/Users/eschenr/Dropbox/WW_SESYNC/data/Soil_data_Baringo/")
# With the code we set up the environment: load required packages and define where the data and outputs are located

rm(list=ls(all=TRUE))

require(nlme)
require(lme4)
require(openxlsx)
require(lmerTest)
require(ggplot2)
require(knitr)
library(reshape)
library(reshape2)
require(plyr)
require(dplyr)

```

```{r load_data, echo=FALSE}
data=read.xlsx("SOC_ALL_results_276_Final_252 RE.xlsx", sheet=1)
data$count<-1
# plot(data[,c(3:8)])
```

We loaded the data to compare SOC in the top 15 cm and the top 100cm.

```{r Puritys_subset, echo=FALSE}
Purity=subset(data,Dataset=="Purity")
Purity2=subset(Purity,Depth==15)
plot(Purity2[,c(3:5,8,10)])
```

We only focus on Purity's data for the moment: is there a relationship between SOC in the top 15cm and total SOC?

```{r plot_data_0, echo=FALSE}
interaction.plot(Purity$Depth,Purity$Landcover,Purity$TotalC015)

# 1 = degraded
# 2 = pristine
# 3 = prosopis_high
# 4 = prosopis_low
# 5 = restored
```

```{r plot_data_1, echo=FALSE}
plot(Total~TotalC015,data=Purity,pch=16,bty="l",las=1,col=as.numeric(as.factor(Purity$Landcover)),cex=as.numeric(as.factor(Purity$Landcover)))

ggplot(data = Purity, aes(x = TotalC015, y = Total, color = Landcover))+       
  geom_point()+stat_smooth(method="lm",se=FALSE)
```

It appears that for some landcover types, there is no relationship between SOC in the top layer and the total SOC content, whereas for other landcover types there is a positive relationship. 

```{r analyse_data, echo=FALSE}
model=Purity2$Total~Purity2$TotalC015*Purity2$Landcover
summary(aov(lm(model)))
head(Purity2)
```
The analysis confirms that there are significant differences in the amount of total SOC stocks among the landcover types but also on the slope of the relationship between total SOC stocks and SOC in the top 15cm. In particular, it seems that SOC stocks in degraded are lower than in restored and and pristine grasslands. In the two Prosopis classes SOC stocks are intermediate. 

```{r plot_data, echo=FALSE}
pairwise.t.test(Purity2$Total,Purity2$Landcover)
barplot(tapply(Purity2$Total,Purity2$Landcover,mean),beside=T,las=1,ylim=c(0,55))+
  arrows(c(0.7,1.9,3.1,4.3,5.5),tapply(Purity2$Total,Purity2$Landcover,mean),c(0.7,1.9,3.1,4.3,5.5),tapply(Purity2$Total,Purity2$Landcover,mean)+tapply(Purity2$Total,Purity2$Landcover,sd)/sqrt(tapply(Purity2$count,Purity2$Landcover,sum)),angle=90)+
  arrows(c(0.7,1.9,3.1,4.3,5.5),tapply(Purity2$Total,Purity2$Landcover,mean),c(0.7,1.9,3.1,4.3,5.5),tapply(Purity2$Total,Purity2$Landcover,mean)-tapply(Purity2$Total,Purity2$Landcover,sd)/sqrt(tapply(Purity2$count,Purity2$Landcover,sum)),angle=90)+
  abline(0,0)
```

```{r summarise_0, echo=FALSE}
mean.SOC100=tapply(Purity2$Total,Purity2$Landcover,mean)
se.SOC100=tapply(Purity2$Total,Purity2$Landcover,sd)/sqrt(tapply(Purity2$count,Purity2$Landcover,sum))
mean.se.SOC100=cbind(mean.SOC100,se.SOC100)
```
